---
title: "Store model summaries and outputs in Parquet"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Store model summaries and outputs in Parquet}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Model functions can return summary statistics and detailed outputs alongside
the distances used by the ABC algorithm. The historical numeric distance
vector remains supported.

```{r, eval=FALSE}
epidemic_model <- function(x, ss_obs) {
  trajectory <- data.frame(
    timestep = rep(1:100, each = 2),
    pop_id = rep(c("A", "B"), 100),
    S = simulate_S(x),
    E = simulate_E(x),
    I = simulate_I(x),
    R = simulate_R(x)
  )

  list(
    distances = c(dist1 = compute_distance(trajectory, ss_obs)),
    summaries = list(
      epidemic_trajectory = trajectory,
      peak_infectious = max(trajectory$I)
    ),
    outputs = list(
      final_state = subset(trajectory, timestep == max(timestep))
    )
  )
}
```

Each element of `summaries` and `outputs` must have a unique name and contain
an atomic vector, a matrix, or a data frame. A tabular object's column names and
types must remain fixed across simulations. The number of rows may vary.

Use separate policies to select which objects are kept:

```{r, eval=FALSE}
result <- abcsmc(
  model_list = list(m1 = epidemic_model),
  prior_dist = prior_dist,
  ss_obs = ss_obs,
  store_summaries = "all",
  store_outputs = "retained"
)
```

Available policies are `"none"`, `"retained"`, `"accepted"`, and `"all"`.
Data are stored below `res/parquet`, separately for each object and generation.

The manifest lists the available datasets:

```{r, eval=FALSE}
list_abc_stored_data(result)
```

Readers can restrict the data by object name, generation, attempt identifier,
or ABC status:

```{r, eval=FALSE}
accepted_trajectory <- read_summary_statistics(
  result,
  name = "epidemic_trajectory",
  generation = 5,
  status = "accepted"
)

rejected_trajectory <- read_summary_statistics(
  result,
  name = "epidemic_trajectory",
  status = "rejected"
)

selected_output <- read_model_outputs(
  result,
  name = "final_state",
  attempt_id = c("g0005-j0001-a000000000003"),
  status = "all"
)
```

The returned tables include `attempt_id`, `generation`, `job_id`, `accepted`,
and `retained`. The `stored_name` column identifies the requested summary or
output when several objects are read together.
